Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

Since geometries are captured by FE, constructed CVs typically extend on each side of the interface which may have different properties. Therefore, average values of coupled velocity-pressure variables are applied across the CVs at the interfaces. This often leads to excessive numerical dispersion especially in highly heterogeneous media. In order to reduce artificial numerical diffusion associated to the upwind weighting of the advected quantity in regions of strong heterogeneity, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}. This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials. A control-volume distributed (CVD) scheme coupled with mixed FEM (MFEM) was introduced by \citet{edwards_2006}, where flow and rock variables are discretised in CV space whereas pressure and velocity are solved in FEM space. CVD flux-limiting scheme was coupled with high-order convection scheme to reduce anisotropic numerical diffusion in flows through semi-impervious barrier  \citep[\ie a region of very low permeability, see also][that solved this particular numerical diffusion problem with the same model used here, originally proposed by \citet{edwards_2006}]{salinas_2018}.

>>>>

Since geometries are captured by FE, constructed CVs typically extend on each side of the interface which may have different properties. Therefore, average values of coupled velocity-pressure variables are applied across the CVs at the interfaces. This often leads to excessive numerical dispersion especially in highly heterogeneous media. In order to reduce artificial numerical diffusion associated to the upwind weighting of the advected quantity in regions of strong heterogeneity, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}. This discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials. Coupled control-volume distributed (CVD) flux-limiting method and high-order convection schemes were introduced by \citet{edwards_2006} to reduce anisotropic numerical diffusion in flows through semi-impervious barriers (\ie flow across regions of large permeability gradient). Solution for such particular numerical diffusion problem was recently revisited by \citet{salinas_2018} using the model formulation outlined in Section~\ref{equations_scheme}.
